---
title: "Why is there a big difference between genders in Juvenile Jail Population?"
output: html_document
---

### Introduction

As in society of where we are living right now, adult crimes are increasing from year to year and we can see that very common on news. But what about youth committing crimes all over the United States? This analysis will focus on the population between different genders in Juvenile Jail. The variables that will be used inside this research are female and male juvenile jail population, year, and state. The reason behind choosing these variables is because I want to explore is there an increasing trend in the population of men in Juvenile prison 

### Summary Information

- In what year did the U.S have the highest male Juvenile population?
- What is the total female Juvenile population in the U.S by the recent date?
- Which state has the lowest juvenile population for males?
- What is the total male Juvenile population in the U.S by the recent date?
- In what year did the U.S have the highest female Juvenile population?

My analysis reflected on the population of female and male Juvenile population in the U.S fromo 1970 to 2018. First when we look at **`highest_male_juvenile_population`** or which year the U.S have the highest male. We get the result of 1993 and the reason behind it might be from the the Juvenile Justice System in which benefit the kids who committed crimes. By taking a closer look at the total female Juvenile population and male in the U.S in 2018 the difference was 3000 juveniles. According to the **`state_lowest_juvenile_male_pop`**, Alabama was the state with the lowest male juveniles populatio, this might be understandable because the law at this state can be lenient towards teenager and protected them from those crime. The last variable was the year which U.S have the highest female Juvenile population. The result suggested that male teenager already commited crime at an earlier age than female teenager.      

### The Dataset

This dataset was created by Vera (Institute of Justice) and information was gathered by the Bureau of Justice Statistics (BJS). It was collected by state departments of correction, the Census of Jails (COJ), Annual Survey of Jails (ASJ). The ASJ, which covers a lot of large jails, has been conducting non-census years since 1982. On the other hand, the COJ has been collecting data on every county since 1970. The data was collected to announce make an emphasis to the public, encourage research, remake the justice policy, and have a better understanding of mass incarceration. There are about 153811 rows and 121 columns in the data. I want to know if there is a bias in the jail population of different races. The first problem to be noted about this data is the amount of NA, making it harder for the one analyzing it to allude out the accurate result. This problem might not be serious to others but to some, they will find this data has too many variables and does not know what to focus on. This data also did not include all genders besides females and males which can cause gender-inclusive problems. After seeing the high contrast in different race jail populations, this can lead to racial issues as in making wrong assumptions of a race based on the jail population.


### Male and Female Juveniles Population Overtime Chart

```{r, echo = FALSE, warning = FALSE, message = FALSE, code = readLines("Chart_1_Genders_Juveniles_Population_Overtime.R")}
```

This chart illustrates the difference in female and male juveniles population overtime from 1970-2018. As you can see from the chart, the number of male juveniles are way over the number of female juveniles. Female juveniles do not exceed half of the male's number. I choose to plot these data on a bar chart to show the big difference in genders for the juveniles population. 


### The juveniles population for both males and females in WY Chart

```{r, echo = FALSE, warning = FALSE, message = FALSE, code = readLines("Chart_2_The_Total_Juveniles_Population_for_Male_and_Female_in_Wyoming.R")}
```

This chart illustrates the juveniles population for both males and females in Wyoming. As you can see from the chart, the number of male juveniles again are way over the number of female juveniles. The reason why I chose Wyoming state because while looking at the incarceration trends data, male and female had a quite similar number of juveniles ppopulation. However when it is plot into a chart, the numbers were too distinct apart, which makes it is easier to see the trend.  


### Map of Female Juveniles Population in 2018

```{r, echo = FALSE, warning = FALSE, message = FALSE, code = readLines("Chart_3_Female_Juveniles_Population.R")}
```

Since there was a very low number in female juveniles Population, I want to know which state has the highest number of female juvenial population. It was interesting to see compared to the highest number of male juvenial population which occurred in every state. The state map shown above stated that there were only three out of 50 states who has female teenagers committing crimes in 2018. There were also five other states however the numbers weren't that significant as New Carolina, Texas, and New York. According to Annie & Cassie Foundation, the Juvenile Justice Reform Act of 2018, this act bands teenagers from entering adult facilities (The Annie E. Casey Foundation, 2018). This might be the reason why teenagers during that time felt risky or challenging to perform crime acts. 
